\item Invited Speaker: Keystone Synthetic Biology eSymposia.  Zoom, (5/3/21).

\item Invited Seminar: Department of Bioengineering, Rice University. Zoom (3/30/21).

\item Plenary Keynote Presentation: BioDesign Research Symposium, Zoom, (12/9/20). 

\item Invited Speaker: CELLS: Workshop on Computing Among Cells, Freiburg, Germany. Zoom, (10/15/20).

\item Invited Seminar: Chemical and Physical Sciences, University of Toronto. Zoom, (9/9/20). 

\item Invited Speaker:  National Academy of Sciences Impact of Physics on Biology Session.  Zoom, (4/2/20).

\item Invited Talk: ONR Naval Biosciences and Biocentric Technologies. Washington, DC (11/18/19). 

\item Invited Talk: Center for Microbiome Innovation, UC San Diego.  San Diego, CA (2/27/19).


\item Invited Seminar: Center for Complex Biological Systems, University of California, Irvine.  Irvine, CA (1/31/19). 

\item Invited Seminar:  La Jolla Institute for Immunology.  La Jolla, CA (1/9/19).

\item Invited Seminar: Center for Synthetic Biology, Northwestern University.  Chicago, IL (11/9/18).

\item Invited Talk:  DARPA Engineered Living Matter.  San Diego, CA (11/7/18). 

\item Invited Seminar:  Department of Bioengineering, Naples University.  Naples, Italy, (9/20/18).

\item Invited Seminar:  Center for Genome Regulation, University of Barcelona.  Barcelona, Spain, (9/18/18).

\item Invited Seminar: Department of Biomedical Engineering, Columbia University. New York, New York, (8/31/18).

\item Invited Talk: Symposium: Frontiers in Single Cell Biology, Sanford Burnham (10/10/17).

\item Invited Talk: International Workshop on Control Engineering and Synthetic Biology,  Royal Academy of Engineering, London,~England~(07/17/17).

\item Invited Seminar: ENS Cachan, Bâtiment d'Alembert, Salle Condorcet, Paris, France (07/25/17).

\item Invited Speaker: The 4th International Workshop on Mammalian Synthetic Biology, Boston, MA (05/06/17).

\item Invited Speaker: The 5th Annual Winter q-bio Meeting, Koloa, Hawaii (02/21/17).

\item Invited Speaker: Institute for Molecular Engineering, University of Chicago, Chicago, IL, (02/02/17).

\item Invited Speaker: SynthSys - Centre for Synthetic and Systems Biology,~University of Edinburgh, Edinburgh, Scotland (07/27/16).

\item Invited Speaker: The 17th Annual UC Systemwide Bioengineering Symposium,~UC San Francisco, San Francisco, CA (06/13/16).

\item Invited Speaker: Quantitative Biology Seminar and Complex Systems Seminar,~University of Michigan, Ann Arbor, MI (03/14/16).

\item Invited Seminar:~Salk Institute, La Jolla, CA (01/20/16).

\item Invited Seminar:~Georgia Tech, Atlanta, GA (11/23/15).

\item Invited Speaker:~Cornell, Ithaca, NY (11/20/15).

\item Invited Speaker: DARPA Workshop, Pasadena, CA (11/1/15).

\item Invited Speaker: Physics of Living Systems, NSF Workshop, Washington DC (11/10/15).

\item Invited Seminar: Salk Institute, La Jolla, CA (09/17/15).

\item Invited Speaker: Qbio, Virginia Tech, Blacksburg, VA (08/05/15).

\item Invited Seminar: Department of Bioengineering, Stanford, Palo Alto, CA (5/4/15).

\item Invited Speaker: DARPA Workshop on Complexity, Wasthington, DC (4/1/4/15).

\item Invited Seminar: Department of Bioengineering, Caltech, Pasadena, CA (11/3/14).

\item  Invited Speaker: Oxford University: Workshop Control Engineering and Synthetic Biology, Oxford, UK (9/12/14).

\item Invited Speaker: Beckman Symposium, National Academy of Sciences, Irvine, CA (7/8/14).

\item Invited Speaker: SEED: Synthetic Biology: Engineering, Evolution, and Design, Manhattan Beach, CA (7/17/14).

\item Invited Speaker: UC Systemwide Bioengineering Symposium, Irvine, CA (6/20/14).

\item Invited Speaker:  DARPA Living Foundries PI Meeting, Denver, CO (6/12/14).

\item Invited Speaker: Center for ChronoBiology, UCSD (2/6/13).

\item Invited Seminar: Department of Cell and Systems Biology, University of Toronto, Toronto, CA (9/20/13).

\item Cold Spring Harbor Computational Cell Biology, Cold Spring Harbor, NY (8/8/13).

\item Invited Seminar: Telethon Institute of Genetics and Medicine, Naples, Italy (7/16/13).

\item Keynote Speaker: Fifth International Workshop on Bio-Design Automation; Imperial College, London, UK (7/13/13).

\item Plenary Lecture: SIAM Applications of Dynamical Systems (Snowbird) Conference (5/23/13).

\item Invited Talk: Keystone Symposia on Precision Genome Engineering and Synthetic Biology (3/21/13).

 \item Invited Seminar: Department of Bioengineering, University of Illinois, Champagne-Urbana (3/7/13).
 
 \item Invited Talk: Symposium: Human Systems Biology and Biotechnology. Johns Hopkins University (11/15/12).

\item Keynote Talk: Imperial College Institute of Systems and Synthetic Biology, Imperial College, London, UK (11/14/12).

\item Invited Talk: Carolina Biophysics Symposium, Raleigh-Durham, NC (11/9/12).

\item Invited Talk: Twenty-fourth Annual Kavli Frontiers of Science Symposium, National Academy of Sciences (11/3/12).

\item Plenary Talk: Model-Based Analysis and Control of Cellular Processes, Purdue University (10/8/12).

\item Invited Seminar: Duke Center for Systems Biology, Raleigh, NC (10/4/12).

\item Invited Talk: Center for Genome Sciences and Systems Biology Symposium, Washington University (9/24/12).

\item Plenary Speaker: ComBio2012, Adelaide Australia (9/26/12).

\item Summer School Lecturer: DNA dynamics and life strategies, Copenhagen, Denmark (8/15/12).

\item Invited Lecture: Cold Spring Harbor Computational Cell Biology, Cold Spring Harbor, NY (7/30/12). 

\item Invited Speaker: UC Systemwide Bioengineering Symposium, Berkeley, CA (6/23/12). 

\item Invited Speaker: Plenary Session on Synthetic Biology, American Society for Microbiology, San Francisco, CA (6/19/12). 

\item Plenary Lecture: Metabolic Engineering IX, Biarritz, France (6/6/12). 

\item Invited Speaker: American Society for Biochemistry and Molecular Biology, San Diego, CA (4/25/12). 

\item Invited Seminar: The Lewis-Sigler Institute For Integrative Genomics, Princeton University (3/12/12). 

\item Invited Speaker: Solvay Meeting, Brussels, Belgium (2/17/12). 

\item Keynote Lecture: University of Hawaii (1/17/12). 

\item Invited Speaker: Dynamics Days 2012, Baltimore, Maryland (1/7/12). 

\item Invited Seminar: The Max Planck Institute, Dresden, Germany (12/1/11). 

\item Invited Seminar: Department of Biochemistry, Rice University, Houston, TX (11/14/11). 

\item Keynote Speaker: Washington University Systems Biology Symposium (10/24/11). 

\item Invited Lecture: Cold Spring Harbor Computational Cell Biology (7/18/11). 

\item Invited Speaker: JASON Workshop, San Diego, CA (7/7/11). 

\item Invited Speaker: BC2 Basel Computational Biology Conference, Basil, Switzerland (6/24/11). 

\item Invited Speaker: UC Systemwide Bioengineering Symposium, Santa Barbara, CA (6/14/11). 

\item Keynote Speaker: Sophia '11 Thematic Research School, Sophia-Antiopolis, France (5/27/11). 

\item Invited Speaker: Keystone Symposia OMICS Meets Cell Biology 2011, Alpbach, Austria (5/9/11). 

\item Invited Speaker: Department of Bioengineering, UCSD (4/29/11). 

\item Invited Speaker: NIH All-Hands Meeting: National Technology Centers for Networks and Pathways, Rockville, MD (4/15/11).

\item Invited Speaker: 8th conference on Computational Cell Biology, Cold Spring Harbor, NY (3/30/11). 

\item Invited Lecture: FEBS Advanced Lecture Course on Systems Biology, Innsbruck, Austria (2/27/11). 

\item Invited Speaker: UCI Systems Biology Conference, Irvine, CA (1/30/11). 

\item Invited Seminar: Department of Biomedical Engineering, Boston University (1/25/11). 

\item Invited Speaker: 3rd International Conference on Biomolecular Engineering, San Francisco, CA (1/17/11). 


\item Plenary Speaker: International Conference on Synthetic Biology: "Bottom-up, Top-down and Cell-free approaches", Paris, France (12/15/10). 

\item Invited Speaker: Dutch Society for Biochemistry and Molecular Biology, Groningen, The Netherlands (11/12/10). 

\item Invited Seminar: Max Planck Institute, Marburg, Germany (11/10/10).

\item Invited Seminar: Department of Pharmacology, UT Southwestern Medical Center, Dallas, TX (10/21/10). 

\item Keynote Lecture: Summer School on Bioengineering, Bressanone, Italy (9/15/10). 

\item Invited Speaker: European Conference on Bacterial Networks (BACNET), San Feliu de Guixols, Spain (9/5/10).

\item Invited Lecture: Cold Spring Harbor Labs, Cold Spring, NY (7/16/10).

\item Invited Seminar: Wyss Institute, Harvard University.  Boston, MA (6/24/10).

\item Invited Seminar: Belgian National Academy of Sciences.  Brussels, Belgium (6/5/10).

\item Invited Speaker: 11th Experimental Chaos and Complexity Conference.  Lille, France (6/3/10).

\item Invited Speaker: Annual Meeting - American Society for Microbiology.  San Diego, CA (5/25/10).

\item Invited Speaker: Workshop on Synthetic Biology and Biomedicine:  Progress, Outlook, and Challenges.  NIH, Bethesda, MD (4/13/10).

\item Invited Seminar: Department of Physiology, Stanford University.  Palo Alto, CA (4/9/10).

\item Invited Speaker: UCSD Center for Chronobiology. San Diego, CA (3/10/10)

\item Invited Seminar: Mathematical Biosciences Institute - Synthetic Biology Workshop, Ohio State University.  Columbus, OH (1/29/10).  

\item Invited Seminar: Department of Pharmacology, University of North Carolina.  Chapel Hill, NC (10/22/09). 

\item Invited Speaker: Center for Systems Biology, Duke University.  Durham, NC (10/21/09).

\item Invited Seminar: Department of Bioengineering, University of California, Berkeley.  Berkeley, CA (9/23/09).  

\item Keynote Talk: Robust Synthetic Biological Parts to Whole Systems.  University of Oxford. Oxford UK (9/15/09).  

\item Invited Lecture: Computational Cell Biology. Cold Spring Harbor Laboratory.  Cold Spring Harbor, NY (7/14/09).

\item Invited Speaker: Nobel Symposium on Systems Biology.  Stockholm, Sweden. (6/24/09).

\item Invited Seminar: Department of Biochemical Engineering.  University College, London.  London, UK (4/30/09).

\item Invited Speaker: Advances in Synthetic Biology.  Select Biosciences.  London, UK (4/28/09). 

\item Invited Speaker: Novel Perspectives of Microfabricated Devices for Systems and Synthetic Biology.  Evry, France (4/3/08).

\item Invited Speaker: European Conference on Synthetic Biology. Sant Feliu de Guixols, Spain (3/30/09).

\item Invited Speaker: Systems Biology: Networks.  Cold Spring Harbor Laboratory.  Cold Spring, NY (3/19/09).

\item Invited Speaker: Dynamics Days. San Diego, CA (1/11/09).

\item Invited Speaker: MD Anderson Symposium on Systems Biology of Cancer. MD Anderson Cancer Center.  Houston, TX (10/30/08). 

\item Invited Speaker: Biomedical Engineering Society (annual meeting).  St. Louis, MO (10/3/08).

\item Invited Seminar: Department of Physics, University of Calgary. Calgary, Ontario (9/12/08).

\item Plenary Talk: Society for Industrial and Applied Mathematics Life Sciences Meeting. Montreal, Quebec (8/7/08).

\item Invited Seminar: Department of Biomedical Engineering, Boston University, Boston, MA (7/14/08).

\item Invited Lecture: Computational Cell Biology. Cold Spring Harbor Laboratory.  Cold Spring Harbor, NY (7/8/08). 

\item Invited Seminar: Departments of Mechanical and Electrical Engineering.  University of California, Santa Barbara. Santa Barbara, CA (5/22/08).

\item Colloquium: Modeling and analysis of biological networks (Transcriptional, Signaling, Metabolic).  Department of Mathematics, University of Houston. Houston, TX (5/15/08). 

\item Invited Speaker: Experimental Biology.  San Diego, CA (04/09/08).

\item Invited Seminar: University of Houston, Department of Mathematics, Houston, TX (03/28/08).

\item Invited Speaker: San Diego Microbiology Group (SDMG).  Scripps Institute of Oceanography, La Jolla, CA (03/19/08).

\item Invited Seminar: Institute for Mathematics and Its Application (IMA).  University of Minnesota, Minneapolis, MN (03/05/08).

\item Invited Speaker: NSF Workshop: System design methodologies.  Washington, DC (02/20/08)


\item Invited Speaker: Deconstructing Biochemical Networks. Montreal, CA (9/25/07).

\item Invited Seminar: Massachusetts Institute of Technology, Department of Chemical Engineering, Boston, MA (9/21/07).

\item Invited Speaker: 1st International q-bio Conference: Information Processing in Cellular Signaling and Gene
Regulation, Santa Fe, NM (8/8/07).

\item Invited Speaker: Society for Mathematical Biology, Annual Meeting, San Jose, CA (7/31/07).

\item Invited Seminar: Georgia Institute of Technology, Department of Biomedical Engineering, Atlanta, GA (6/25/07).

\item Invited Speaker: Institute for Biological Engineering 12th Annual Meeting, St. Louis, MO (3/31/07).

\item Invited Speaker: American Physical Society (APS) March Meeting, Denver, CO (3/5/07).

\item Invited Seminar: University of Washington Department of Bioengineering,
Seattle, WA (2/26/07).

\item Invited Seminar: University of Pennsylvania Department of Bioengineering,
Philadelphia, PA (1/18/07).

\item Invited Seminar: Fred Hutchinson Cancer Research Center, Seattle, WA (9/26/06).

\item Invited Speaker: Society for Industrial and Applied Mathematics (SIAM) 2nd Life
Science Conference, Raleigh, NC (7/31/06).


\item Invited Speaker: American Association for Microbiology and IEEE Engineering
in Medicine and Biology Society: Bio-, Micro-, Nanosystems, San
Francisco, CA (1/17/06).


\item Invited Speaker: IEEE International Workshop on Genomic Signal Processing and
Statistics, Newport, RI (5/22/05).

\item Invited Speaker: Computational Physiology: From Genome to Physiome, San Diego,
CA (3/29/05).

\item Invited Speaker: Biomedical Engineering Society (BMES) annual meeting, Philadelphia, PA (10/15/04).

\item Invited Speaker: Bioinformatics 2004, Linkoping, Sweden (6/5/04).

\item Invited Speaker: Workshop on Genomic Signal Processing and Statistics.  Johns Hopkins University, Baltimore,
MD (5/26/04)

\item Invited Seminar: Center for Theoretical Biophysics, UCSD (3/9/04).

\item Invited Speaker: American Physical Society March Meeting.  Montreal, Quebec
(3/21/04).

%Engineered Gene Circuits:  A Playground for Physicists and Applied
%Mathematicians,
\item Invited Speaker: American Physical Society, Opportunities in
Biology for Physicists, San Diego, CA (1/30/04).

%Engineered gene circuits.
\item Invited Seminar: Department of Biology, The Georgia Institute of Technology,
Atlanta, GA (1/27/04).

%Engineered gene circuits.
\item Invited Seminar: Material Sciences Department. University of Tennessee, Knoxville (1/26/04).

\item Invited Speaker: National Academy of Sciences Keck Futures Initiative, Irvine, CA (11/15/03).

\item Invited Seminar: Institute for Systems Biology, Seattle,
WA (10/07/03).

\item Invited Speaker: Pathways, Networks, and Systems:
Theory and Experiments, Santorini, Greece (10/01/03).

\item Invited Seminar: UCSD Department of Bioengineering,
La Jolla, CA (05/09/03).

\item  Invited Speaker: American Physical Society March
Meeting, Austin, TX (03/06/03).

\item  Invited Speaker: UCSD Jacobs School of Engineering
Research Review, La Jolla, CA (02/28/03).

\item  Invited Speaker: UCSD Molecular Biophysics Training
Grant Retreat, La Jolla, CA (02/15/03).

\item  Invited Speaker: O'Reilly Bioinformatics
Technology Conference, San Diego, CA (02/04/03).

\item Invited Speaker: American Mathematical Society (AMS) national
meeting (01/15/03).

\item Invited Speaker: Stochastic fluctuations in gene regulation.
DARPA BioCOMP PI meeting, San Diego, CA (12/10/02).

%A reductionist approach to systems biology: {\em In numero}
%predictions, {\em in vivo} dynamics.
\item  Invited Seminar: Advanced Studies Institute, Australian National University, Canberra, AU (10/23/02).

%Designer gene networks: {\em De novo} constructs -- {\em in
%numero} descriptions.
\item Invited Speaker: SIAM workshop on Computational Models and
Simulation for Intra-Cellular Processes, Washington, DC
(10/04/02).

%Engineered gene circuits for biocomputing applications.
\item Invited Speaker: Institute for Pure and Applied Mathematics workshop: Mathematics
in Nanoscale Science and Engineering, University of California,
Los Angeles, CA (10/1/02).

%Designer gene networks: {\em De novo} constructs -- {\em in
%numero} descriptions.
\item Invited Speaker: Center for Biodynamics Minisymposium:
Dynamics of Gene Expression, Boston University, Boston, MA
(04/26/02).

%Designer gene networks: {\em De novo} constructs -- {\em in numero}
%descriptions.
\item Invited Seminar: Department of Applied Mathematics, State
University of New York at Stony Brook, Stony Brook, NY (04/24/02).

%Designer gene networks: {\em De novo} constructs -- {\em in numero}
%descriptions.
\item Invited Seminar: Department of Bioengineering, California
Institute of Technology, Pasadena, CA (03/13/02).

%Designer gene networks.
\item Invited Speaker: Society for Industrial and Applied Mathematics (SIAM) 1st Life
Science Conference, Boston, MA (03/06/02).

%Designer gene networks: {\em De novo} constructs -- {\em in numero}
%descriptions.
\item Invited Seminar: Department of Biomedical Engineering,
University of Minnesota, Minneapolis, MN (02/11/02).

%Designer gene networks: {\em De novo} constructs -- {\em in numero}
%descriptions.
\item  Invited Seminar: Department of Bioengineering, University of
California, San Diego, CA (02/01/02).

%Designer gene networks: {\em De novo} constructs -- {\em in numero}
%descriptions.
\item  Invited Seminar: Department of Applied Physics and Applied
Mathematics, Columbia University, New York, NY (01/29/02).

%Designer gene networks: {\em De novo} constructs -- {\em in numero}
%descriptions.
\item Invited Seminar: Department of Biengineering, University of
Pennsylvania, Philadelphia, PA (01/24/02).

\item Invited Speaker: Designer gene networks: {\em De novo} constructs -- {\em in
numero} descriptions.  DARPA BioCOMP PI meeting, Monterey, CA
(11/28/01).

\item Invited Speaker: Designer gene networks: {\em De novo} constructs -- {\em in
numero} descriptions.  NSF QuBIC PI meeting, Monterey, CA
(11/28/01).

%Designer gene networks: {\em De novo} constructs -- {\em in numero}
%descriptions.
\item Invited Seminar: Department of Biomedical Engineering,
University of California, Davis, CA (11/05/01).

%Designer gene networks: {\em De novo} constructs -- {\em in numero}
%descriptions.
\item  Invited Seminar: Virginia Bioinformatics Research Institute
and the Virginia Institute of Technology, Blacksburg, VA
(12/14/01).

%{\em In numero} and {\em in vivo} studies of {\em de novo} synthetic
%gene networks in Escherichia coli.
\item Invited Seminar: Department of Biomedical Engineering, University of Massachusetts
Medical School, Worcester, MA (10/15/01).

%Designer gene networks.
\item Invited Seminar: Center for Neurodynamics and Department of Physics, University
of Missouri, St. Louis, MO (07/10/01).

%{\em In numero} molecular biology.
\item Invited Seminar: Center for Nonlinear
Dynamics and Dept. of Physiology, McGill University, Montreal,
Quebec (06/05/01).

%Designer gene networks.
\item Invited Speaker: Society for Industrial
and Applied Mathematics (SIAM) 6th Conference on Applications of
Dynamical Systems, Snowbird, UT (05/22/01).

%Designer gene networks.
\item Invited Seminar: Center for Nonlinear
Dynamics and Dept. of Physiology, McGill University, Montreal,
Quebec (12/20/00).

%Designer gene networks.
\item Invited Seminar: Department of Biomedical Engineering,
The Johns Hopkins University, Baltimore, MD (12/12/00).

%Noise-based control of gene expression.
\item Invited Seminar: Biology Department,
The Virginia Institute of Technology, Blacksburg, VA (04/18/00).

%Gene regulation for nonlinear dynamicists.
\item Invited Speaker: Center for
Biodynamics, Boston University, Boston, MA (03/09/00).

%Noise-based control of gene expression.
\item Invited Seminar: Center for
Interdisciplinary Research on Complex Systems, Northeastern
University, Boston, MA (01/25/00).